---
title: "Seminar OSE"
author: "Pascal Mounchid"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r}
library(haven)
library(tidyverse)
library(cregg)
library(readxl)
library(openxlsx)
library(lubridate)
```

```{r}
setwd("C:/Users/Pasca/OneDrive/8.Semester/Seminar Susumu")
```

```{r}
raw <- read.csv('all_apps_wide-2022-09-12_1004.csv', header=T)
raw[['participant.time_started_utc']] <- strptime(raw[['participant.time_started_utc']],
                                                  format = '%Y-%m-%d %H:%M:%OS',
                                                  tz = 'utc')
op <- options(digits.secs=6)
#attr(raw$participant.time_started_utc, 'tzone') <- 'CET'
#with_tz(raw$participant.time_started_utc, "CET")
as.POSIXlt(raw$participant.time_started_utc, tz = 'CET')
```

Cleaning 2.0

```{r}
# drop observations 
raw1 <- raw %>% filter(participant._is_bot !=1  # recognised as bot
                        ,survey_example_appfolder.1.player.time_welcome != -999  # did not start survey
                        ,survey_example_appfolder.1.player.time_endpage != -999  # did not end survey
                        , ! is.na(participant.label) # no participant label
                        )
```

Data Formatting
```{r}
raw1 <- raw1 %>% mutate( #convert times
                          survey_example_appfolder.1.player.time_welcome =
                          as.POSIXlt(survey_example_appfolder.1.player.time_welcome, 
                                   format = '%Y-%m-%dT%H:%M:%S',
                                   tz = 'utc')
                        , survey_example_appfolder.1.player.time_quotapage =
                          strptime(survey_example_appfolder.1.player.time_quotapage, 
                                   format = '%Y-%m-%dT%H:%M:%S',
                                   tz = 'utc')
                        , survey_example_appfolder.1.player.time_endpage =
                          strptime(survey_example_appfolder.1.player.time_endpage, 
                                   format = '%Y-%m-%dT%H:%M:%S',
                                   tz = 'utc')
                        , survey_example_appfolder.1.player.sm_time_treatmentpage =
                          strptime(survey_example_appfolder.1.player.sm_time_treatmentpage, 
                                   format = '%Y-%m-%dT%H:%M:%S',
                                   tz = 'utc')
                        , survey_example_appfolder.1.player.sm_time_demonstrationpage =
                          strptime(survey_example_appfolder.1.player.sm_time_demonstrationpage, 
                                   format = '%Y-%m-%dT%H:%M:%S',
                                   tz = 'utc')
                        , survey_example_appfolder.1.player.sm_time_participationpage =
                          strptime(survey_example_appfolder.1.player.sm_time_participationpage, 
                                   format ='%Y-%m-%dT%H:%M:%S',
                                   tz = 'utc')
                        , survey_example_appfolder.1.player.sm_time_politicalpage =
                          strptime(survey_example_appfolder.1.player.sm_time_politicalpage, 
                                   format = '%Y-%m-%dT%H:%M:%S',
                                   tz = 'utc')
                        # rename variables before dropping ba/ch variables
                        , location = survey_example_appfolder.1.player.ba_location
                        , immigration1 = survey_example_appfolder.1.player.ba_immigration1
                        , immigration2 = survey_example_appfolder.1.player.ba_immigration2
                        , immigration3 = survey_example_appfolder.1.player.ba_immigration3) 
# time needed for the full survey
raw1$starttofinish <- raw1$survey_example_appfolder.1.player.time_endpage -
                      raw1$survey_example_appfolder.1.player.time_welcome 
save(raw1, file = "raw_all.RData")
```

```{r}
# drop all variables of other groups
columns_ba <- grep("survey_example_appfolder.1.player.ba", names(raw1))
raw2 <- raw1 %>% select(-columns_ba) 
columns_ch <- grep("survey_example_appfolder.1.player.ch", names(raw2))
raw2 <- raw2 %>% select(-columns_ch) 
# drop prefix from column names
names(raw2) <- sub('^survey_example_appfolder.1.player.', '', names(raw2))
save(raw2, file = "raw_no_ba_ch.RData")
```

```{r}
# convert social movement and other relevant variables to factors
raw3 <-raw2 %>% mutate(across(
                              c(sm_group_assignment,
                                sm_participation ,
                                sm_topic_relevance,
                                sm_familiar_people,
                                sm_booked,
                                sm_transportation,
                                sm_reach,
                                sm_number,
                                sm_crowd,
                                sm_polarization,
                                sm_riots,
                                sm_missing_knowledge,
                                sm_own_knowledge,
                                sm_general_knowledge,
                                sm_future,
                                sm_unsure,
                                sm_olddays,
                                sm_demonstration_change,
                                sm_demonstration_democracy,
                                sm_demonstration_views,
                                sm_politicians,
                                sm_influence,
                                sm_interests,
                                therm_spd,
                                therm_cdu,
                                therm_csu,
                                therm_gruene,
                                therm_fdp,
                                therm_afd,
                                therm_linke,
                                household_income,
                                general_education,
                                eligibility,
                                participation,
                                demonstration_participation_allowed,
                                demonstration_participation_notallowed,
                                demonstration_participation_online,
                                social_media,
                                device_type,
                                operating_system),
                              as.factor))
                                  
save(raw3, file = "raw_factor.RData")
# turn missing (-999) and "weiß nicht" (-888) answers to NA
df <- raw3 %>% mutate(across(where(is.factor), ~na_if(., -999)),
                        across(where(is.factor), ~na_if(., -888)))
save(df, file = "online_exp_df.RData")
```
Reduce the variables 

```{r}
Data_Full <- df %>% 
  select(age, 
         gender, 
         federalstate, 
         starts_with("sm"), 
         starts_with("therm"), 
         sm_own_knowledge,
         sm_general_knowledge, 
         social_media,
         sm_demonstration_change, 
         sm_demonstration_democracy, 
         demonstration_participation_online) %>% 
                          add_column(ID = seq(1:1166)) 

Data_Full <- Data_Full %>% 
    mutate(Age2 = 2022 - age) %>%
```


```{r}
filter(Age2 %in% (18:100)) 

Data_Full <- Data_Full %>% 
  rename(Treatmentgroup = sm_group_assignment,
         Participation_Likelihood = sm_participation)

Data_Full <- Data_Full %>% 
  drop_na(Participation_Likelihood)


table(Data_Full$sm_own_knowledge) 
```

- All respondents with no answer on likert scale are deleted

```{r}
Data_Full$Treatmentgroup <- as.factor(Data_Full$Treatmentgroup)
Data_Full$Participation_Likelihood <- as.numeric(Data_Full$Participation_Likelihood)
```


```{r}
Data_Full$Treatmentgroup <-  recode_factor(Data_Full$Treatmentgroup, "1" = "Low Likes", "2" = "Intermediate Likes", "3" = "High Likes") 

Data_Full$Treatmentgroup <- relevel(Data_Full$Treatmentgroup, ref = "Low Likes")
```


```{r}
amces <- cj(Data_Full, Participation_Likelihood ~  Treatmentgroup, id = ~ID)
head(amces[c("feature", "level", "estimate", "std.error")], 20L)
```
## AMCE Calculation for main effects

```{r}
amcesplot <- plot(amces, size = 2)

AMCE_Hauptanalyse <- amcesplot +
  scale_colour_grey(end = 0) + 
  theme_bw()+
    labs(title = "Effects of different treatments on the likelihood for participation at a demonstration",
         x = "Estimated AMCE",  
         caption = "Sample size : 1053 respondents.") +
          theme(text=element_text(size=11), legend.position = 'none') +
                theme(plot.caption = element_text(hjust = 0, face= "italic"), 
                  plot.title.position = "plot", 
                  plot.caption.position =  "plot") 
 
AMCE_Hauptanalyse

ggsave("AMCE_Hauptanalyse.png", width = 19, height = 27, units = "cm")

```


## Marginal Means for the main effects

```{r}
MarginMeans <- cj(Data_Full,
                  Participation_Likelihood ~  Treatmentgroup,
                  id = ~ID,
                  estimate = "mm")
```


```{r}
Plot1_MainA <-plot(MarginMeans, size = 2) + 
   theme(legend.position = "none") +
              labs(title= "Marginal Means for the individual treatment effects", 
                   caption = "Sample size = 1053.")+
      scale_color_grey(end = 0) +
                  theme_bw() +
                      theme(text=element_text(size=11), legend.position = 'none') +
                        theme(plot.caption = element_text(hjust = 0, face= "italic"), 
                        plot.title.position = "plot", 
                        plot.caption.position =  "plot") 


Plot1_MainA

ggsave("Plot1_MainA.png", width = 19, height = 27, units = "cm")
```

#Age Subgroup Analysis

I. Data cleaning and subgroup management

```{r}
Data_Full <- Data_Full %>% 
 mutate(Agegroup = case_when(Age2 >= 18  & Age2 <= 38 ~ "18-38",
                             Age2 >= 39  & Age2 <= 59 ~ "39-59",
                            Age2 >= 60  & Age2 <= 79 ~ "60-79")) 

table(Data_Full$Agegroup)

Data_Full$Agegroup <- as.factor(Data_Full$Agegroup)
```


```{r}
mm_age <- cj(Data_Full, Participation_Likelihood ~  Treatmentgroup, id = ~ID, estimate = "mm", by = ~Agegroup)
```

Plot for the figure

```{r}
Plot_Marginal_Age <-plot(mm_age,
                         group = "Agegroup", na.rm=TRUE, size = 2)+
                            labs(title= "Subgroupanalysis for age groups", 
                                 caption =  "Sample size 1053.\n 18-38 Years: 391 respondents.\n 39-59 Years: 370 respondents.\n 60-79 Jahre: 292 respondents ") +
                      theme(legend.position = "right") +
  theme_bw()+
          theme(text=element_text(size=11)) +
                theme(plot.caption = element_text(hjust = 0, face= "italic"), 
                  plot.title.position = "plot", 
                      plot.caption.position =  "plot") +
                            scale_colour_brewer(palette="Set1") 


Plot_Marginal_Age

ggsave("Plot_Marginal_Age.png", width = 19, height = 27, units = "cm")


```

#### Subgroup party affiliation


```{r}
Data_Full <- Data_Full %>%
        pivot_longer(names_to = "partei",
                     values_to = "values",
                            therm_spd:therm_linke) %>%
                                          group_by(ID) 

Data_Full$values <- as.numeric(Data_Full$values)



Data_Full <- Data_Full %>%
          filter(values == max(values)) %>%
                      slice_sample(n = 1) %>%
          mutate(partei = str_remove(partei, "therm_")) %>%
          select(-values) %>%
                  ungroup() 
          mutate(across(contains("player.random"), factor))

class(Data_Full$partei)

table(Data_Full$partei)

Data_Full$partei <- as.factor(Data_Full$partei)
```


## Calculation of Marginal Means

```{r}
mm_party <- cj(Data_Full, Participation_Likelihood ~  Treatmentgroup, id = ~ID, estimate = "mm", by = ~partei)
```

## Figure for party affiliation

```{r}
Plot_Marginal_Party <-plot(mm_party,
                         group = "partei", na.rm=TRUE, size = 2)+
                              labs(title= "Subgroupanalysis for political partys", 
                                   caption = "Sample size 1020.\n afd: 146, cdu/csu: 225, fdp: 104, gruene: 213,  linke: 114, spd: 218") +
  theme(legend.position = "right") +
    theme_bw()+
          theme(text=element_text(size=11)) +
                theme(plot.caption = element_text(hjust = 0, face= "italic"), 
                  plot.title.position = "plot", 
                      plot.caption.position =  "plot") +
                          scale_colour_brewer(palette="Set1") 


Plot_Marginal_Party

ggsave("Plot_Marginal_Party.png", width = 19, height = 27, units = "cm")


```

####
Marginal Means: Subgroup: "Im Allgemeinen weiß ich wenig über Politik"
######

```{r}
Data_Full$sm_own_knowledge <- as.factor(Data_Full$sm_own_knowledge)

Data_Full <- Data_Full %>% 
  rename(Political_Knowledge=sm_own_knowledge)
       
table(Data_Full$Political_Knowledge)    
class(Data_Full$Political_Knowledge) 

Data_Full$Political_Knowledge <-  recode_factor(Data_Full$Political_Knowledge,
                                                "1" = "Disagree", 
                                                "2" = "Partly-Disagree",
                                                "3" = "Intermediate",
                                                "4" = "Partly-Agree",
                                                "5" = "Agree"
                                                ) 

Data_Full$Political_Knowledge <- factor(Data_Full$Political_Knowledge,
                                        levels = c("Agree", 
                                                   "Partly-Agree", 
                                                   "Intermediate", 
                                                   "Partly-Disagree", 
                                                   "Disagree"))

table(Data_Full$Political_Knowledge)

```

###  Marginal Means: Calculation political knowledge

```{r}
mm_polknow <- cj(Data_Full, 
                 Participation_Likelihood ~ Treatmentgroup, 
                 id = ~ID, 
                 estimate = "mm", 
                 by =~Political_Knowledge)
```

## Plot for the item about subjectiv political knowledge

```{r}
Plot_Marginal_Polk <-plot(mm_polknow,
                            group = "Political_Knowledge", na.rm=TRUE, size = 2)+
                                    labs(title= "Subgroupanalysis for Item",
                                         subtitle= "Generally, I know little about politics...", 
                                         caption = "Sample size 1053.\n Agree: 89 respondents \n Partly-Agree: 160 respondents\n Intermediate: 251 respondents\n Partly-Adisagree: 272 respondents\n Disagree: 235 respondents") +
  theme(legend.position = "right") +
      theme_bw()+
          theme(text=element_text(size=11)) +
                theme(plot.caption = element_text(hjust = 0, face= "italic"), 
                  plot.title.position = "plot", 
                  plot.caption.position =  "plot") +
                    scale_colour_brewer(palette="Set1") 


Plot_Marginal_Polk

ggsave("Plot_Marginal_Polk.png", width = 19, height = 27, units = "cm")


```



####
Marginal Means: Subgroup: "Durch Demonstrationen koennen
keine politischen Veraenderungen bewirkt werden."
######


```{r}
Data_Full$sm_demonstration_change <- as.factor(Data_Full$sm_demonstration_change)

Data_Full <- Data_Full %>% 
  rename(Demonstration_Change=sm_demonstration_change)
       
table(Data_Full$Demonstration_Change)    
class(Data_Full$DDemonstration_Change) 

Data_Full$Demonstration_Change <-  recode_factor(Data_Full$Demonstration_Change,
                                                "1" = "Disagree", 
                                                "2" = "Partly-Disagree",
                                                "3" = "Intermediate",
                                                "4" = "Partly-Agree",
                                                "5" = "Agree"
                                                ) 

Data_Full$Demonstration_Change <- factor(Data_Full$Demonstration_Change,
                                        levels = c("Agree", 
                                                   "Partly-Agree", 
                                                   "Intermediate", 
                                                   "Partly-Disagree", 
                                                   "Disagree"))

table(Data_Full$Demonstration_Change)

```


```{r}
mm_demo <- cj(Data_Full, 
                 Participation_Likelihood ~ Treatmentgroup, 
                 id = ~ID, 
                 estimate = "mm", 
                 by =~Demonstration_Change)
```

### Plot for the item about demonstraion change

```{r}
Plot_Marginal_change <-plot(mm_polknow,
                         group = "Demonstration_Change", na.rm=TRUE, size = 2)+
                                  labs(title= "Subgroupanalysis for Item",
                                       subtitle= "Demonstrations cannot bring any political change...", 
                                       caption = "Sample size 1053.\n Agree: 140 respondents \n Partly-Agree: 182 respondents\n Intermediate: 259 respondents\n Partly-Adisagree: 220 respondents\n Disagree: 224 respondents") +
  theme(legend.position = "right") +
  theme_bw()+
          theme(text=element_text(size=11)) +
                theme(plot.caption = element_text(hjust = 0, face= "italic"), 
                    plot.title.position = "plot", 
                      plot.caption.position =  "plot") +
                          scale_colour_brewer(palette="Set1") 


Plot_Marginal_change

ggsave("Plot_Marginal_change.png", width = 19, height = 27, units = "cm")


```
## Plotting frequency of the treatment group



```{r}
MarginMeans <- Participation_Likelihood ~  Treatmentgroup

MarginMeans <- as.data.frame(MarginMeans)
                  
PlotFreq <- plot(cj_freqs(Data_Full, MarginMeans, id = ~ID))


ggsave("PlotFreq.png")
```


##Barplot about Online participation and agegroup

```{r}

PartA <- Data_Full %>% 
  select(Agegroup, demonstration_participation_online) %>% 
  drop_na(demonstration_participation_online) 

DataPart <- table(PartA$demonstration_participation_online, PartA$Agegroup)

DataPart <- as.data.frame(DataPart)

DataPart <- DataPart %>% 
  filter(Var1 != -999) %>% 
  rename(Participation_Demo_Online=  Var1,
         Agegroup = Var2)

DataPart$Participation_Demo_Online <-  recode_factor(DataPart$Participation_Demo_Online,
                                                "1" = "Yes", 
                                                "2" = "No") 


ggplot(DataPart, aes(x = factor(Agegroup), y = Freq  , fill = Participation_Demo_Online, colour = Participation_Demo_Online)) + 
  geom_bar(stat = "identity", position = "dodge")
```




























